---
title: Places Leaflet
author: nelvis
date: '2020-11-02'
slug: places-leaflet
categories:
  - Code
tags:
  - R
description: ''
dropCap: no
displayInMenu: no
displayInList: yes
resources:
  name: featuredImage
  src: ''
  params:
    description: ''
---

More code: the map in the places page is built through the R library leaflet and via openstreetmap. The extra ingredient is a dataset with places - latitude, longitude and a description. Mine is [here](https://raw.githubusercontent.com/naelvis/refactored-happiness/rstudio/content/post/data/places.csv).

The code looks like this:

```{r eval = FALSE}
leaflet(width = "100%") %>%
  addTiles() %>%
  addCircleMarkers(
    data = Map,
    lng = ~ Longitude,
    lat = ~ Latitude,
    popup = ~ Label,
    fillColor = ~ Color,
    clusterOptions = markerClusterOptions()
  ) %>% 
  addLegend(position = "bottomright", 
            pal = colorFactor(
              viridis(
                length(unique(Map$Type))),
              Map$Type), 
            values = Map$Type, 
            labels = "Labels", 
            title = "What?")
```

It's a single pipe, nothing spectacular happens. Maybe more interesting: I had initially generated the map on Google Maps, when I wanted to download it from there I had to massage it a bit. Code:

```{r eval = FALSE}
Map <- st_layers("places.kml") %>%
  {map_dfr(.$name,
           ~ {read_sf("places.kml",
                      layer = .x) %>%
               mutate(Type = .x)})} %>% 
  cbind(st_coordinates(.)) %>% 
  unclass() %>% 
  as.data.frame() %>% 
  select(Name, Type, X, Y) %>% 
  rename(Longitude = X, Latitude = Y) %>% 
  mutate(Type = fct_relevel(Type, "Other", after = Inf),
         Color = colorFactor(
                  viridis(
                    length(unique(.$Type))),
                    .$Type)(.$Type),
         Label = str_c("<b>", Name, "</b>"))

```

This is a bit more complex, quite largely trial and error on my side. The only lasting takeaway is knowledge about the library [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html).